I would like to first thank my amazing, beautiful wife who puts up with my nonsense. Shout out to Baby Jay, even though he was a late arrival to this party. When I come home from a long day at the lab and see the smile on his little face, I just know he's about to jab me with something.

There is no better PhD advisor than Douglas Densmore. He taught me the one little word that will get me through academic life and beyond: \emph{tranquillo}. Like me, he understands that sometimes in life you only get to order one \emph{primi} [sic]. In all seriousness, I have yet to describe my PhD experience to anyone without inducing some serious PI envy. Thank you for everything and I will cherish the days you allowed me to spend in your lab. Thanks to the Fluigi crew (Josh, Krishna, Ali) and Prashant for always getting me home safe and on-time.

Special thanks to Jason Holder, who pushed me to develop a thesis of which I can be proud. Thank you for letting me be a part of your lab and your team. What can I say about the Acoustic Boyz? Thanks to Parker Dow for teaching me everything I know; thanks to Charlie Lissandrello for the dusty lemonade; apologies to Ryan Dubay, I blame it on the economy; thanks to Ken ``Doctor'' Kotz for your curiosity in my project by asking me every day if it's working; thanks to Peter, David, Chris and Helen for granting me four square feet in the productivity hub known simply as ``The Pitt''; thanks to Jac, Sarah, and Sammy G. for staying up until 4am on a work night; thanks to Jason Fiering for allowing me to distract his best workers.


Shout out to my funding agency and my employer, the United States Air Force, where, maybe, just once, someone will call me ``Sir'' without adding, ``You're making a scene.''
