\addcontentsline{toc}{chapter}{Curriculum Vitae}

{\centering
\huge
\textbf{Curriculum Vitae}\\
\Large
\hspace{1cm}  \\
\textbf{Ryan Silva}

\normalsize
610 Commonwealth Ave.

Boston University

Boston, MA 02215

rjsilva@bu.edu\\[1cm]
}
\large
\textbf{Education}\\
\rule{\textwidth}{1pt}

\begin{table}[h!]
\centering
\small
\begin{tabular}{ p{9.5cm} p{2.5cm} p{4.5cm}}
	\multicolumn{3}{l}{\textbf{Boston University, Boston, MA 02215}}\\
	PhD, Electrical and Computer Engineering & GPA: 4.0/4.0 & 2014 - 2017\\
	\multicolumn{3}{l}{\textbf{Advisor: }Douglas Densmore}\\
	\multicolumn{3}{l}{\textbf{Thesis: }MakerFluidics: Low Cost Microfluidics for Synthetic Biology}\\
	 & & \\
	\multicolumn{3}{l}{\textbf{Air Force Institute of Technology (AFIT), Dayton, OH, 45433}}\\
	Master of Engineering, Electrical Engineering & GPA: 3.8/4.0 & 2005 - 2007\\
	\multicolumn{3}{l}{\textbf{Advisor: }Rusty Baldwin}\\
	\multicolumn{3}{l}{\textbf{Thesis: }Optimizing the Advanced Encryption Standard for an 8-bit Datapath}\\
	 & & \\
	\multicolumn{3}{l}{\textbf{United States Air Force Academy (USAFA), Colorado Springs, CO, 80841}}\\
	Bachelor of Science, Electrical Engineering & GPA: 3.7/4.0 & 2002 - 2005\\
\end{tabular}
\end{table}

\large
\textbf{Awards}\\
\rule{\textwidth}{1pt}

\begin{table}[h!]
\centering
\small
\begin{tabular}{ p{12.5cm} p{4.5cm}}
	Charles Stark Draper Laboratory Fellow & 2016 - 2017 \\
	USAFA Faculty Pipeline Fellow & 2014 - 2017 \\
	Great Minds in STEM Most Promising Engineer & 2013 \\
	IEEE Design Excellence Award & 2013 \\
	Outstanding Academy Educator & 2013
\end{tabular}
\end{table}

\large
\textbf{Professional Affiliations}\\
\rule{\textwidth}{1pt}

\begin{table}[h!]
\centering
\small
\begin{tabular}{ p{12.5cm} p{4.5cm}}
	Association for Computing Machinery VLSI (ACMVLSI) & Reviewer 2017 \\
	American Society of Engineering Education (ASEE) & Member 2011 \\
	Tau Beta Pi - National Engineering Honor Society & Inducted 2006\\
	Eta Kappa Nu - National Electrical Engineering Honor Society & Inducted 2006\\
	Institute of Electrical and Electronics Engineers (IEEE) & Member 2004 \\
	United States Air Force Academy Association of Graduates (USAFA AOG) & Member 2001
\end{tabular}
\end{table}

\newpage

\large
\textbf{Publications}\\
\rule{\textwidth}{1pt}

\small
\begin{enumerate}
	\item{R. Dubay, \textbf{R. Silva} and J. Fiering, ``High Throughput Acoustophoresis in an Array of Parallel Plastic Microchannels'' Acoustofluidics 2017.}
	\item{\textbf{R. Silva}, P. Dow, R. Dubay, C. Lissandrello, J. Holder, D. Densmore and J. Fiering, ``Rapid prototyping and parametric optimization of plastic acoustofluidic devices for blood--bacteria separation'' Biomedical Microdevices 2017.}
	\item{\textbf{R. Silva}, S. Bhatia, and D. Densmore, ``A reconfigurable continuous-flow fluidic routing fabric using a modular, scalable primitive,'' Lab on a Chip 2016.}
	\item{\textbf{R. Silva}, R. Sanka and D. Densmore, ``MakerFluidics: Microfluidics for the Masses'' Eighth International Workshop on Bio-Design Automation (IWBDA) 2016.}
	\item{\textbf{R. Silva}, A. Heuckroth, H. Huang, A. Rolfe and D. Densmore, ``MakerFluidics: Microfluidics for All'', SynBERC 2015.}
	\item{P. Vaidyanathan, B. Der, S. Bhatia, N. Roehner, \textbf{R. Silva}, C. Voigt and D. Densmore, ``A Framework for Genetic Logic Synthesis.'' Proceedings of the IEEE 2015.}
	\item{H. Huang, A. Heuckroth, \textbf{R. Silva}, S. Bhatia, and D. Densmore, ``Fluigi: An Automated Framework for Creating Bioelectronic Devices", Seventh International Workshop on Bio-Design Automation (IWBDA), 2015.}
	\item{A. Pacheco, \textbf{R. Silva}, S. Iverson, T. Haddock and D. Densmore, ``Multicellular Logic through Conversion of Genetic Circuit Outputs into Electrical Signals'', SynBERC 2015.}
	\item{A. Heuckroth, H. Huang, \textbf{R. Silva}, S. Iverson, T. Haddock, A. Pacheco, and D. Densmore, ``Accessible microfluidic mold fabrication using 3d printing", SynBERC 2015.}
	\item{C. Hendrix, D. Neebel and \textbf{R. Silva}, ``A Breadth First Course in Electrical and Computer Engineering.'' ASEE 2014.}
	\item{M. Roberts, R. Deppensmith and \textbf{R. Silva}, ``Observations from First-Year Instructors: What We Wish We Knew Before We Began.'' ASEE 2012.}
	\item{\textbf{R. Silva}, ``Implementation and Optimization of the Advanced Encryption Standard Algorithm using an 8-bit Datapath'', Defense Technical Information Center 2007.}
\end{enumerate}

\newpage

\large
\textbf{Invited Talks}\\
\rule{\textwidth}{1pt}

\small
\begin{itemize}
	\item ``\textit{MakerFluidics: Microfluidics for the Masses}'' \\2nd Workshop on Molecular Communications\\Dublin, Ireland 9 May 2017
\end{itemize}


\large
\textbf{Teaching Experience}\\
\rule{\textwidth}{1pt}

\begin{table}[h!]
\centering
\small
\begin{tabular}{ p{12.5cm} p{4.5cm}}
	\textbf{United States Air Force Academy}, Assistant Professor of ECE& \\
ECE382 Embedded Systems I, Course Director& AY2012-2014\\
ECE281 Digital Design and Computer Architecture, Course Director & AY2012-2014\\
ECE210 Principles of Air Force Electronic Systems(Maj), Course Director & AY2013-2014\\
ECE315 Principles of Air Force Electronic Systems(Core), Instructor & AY2011-2013\\
ENGR101 Introduction to Air Force Engineering, Instructor & AY2012-2014\\
ECE463/464 Capstone Design Project, Mentor & AY2012-2014
\end{tabular}
\end{table}

\large
\textbf{Patents}\\
\rule{\textwidth}{1pt}

\small
\begin{itemize}
	\item{J. Fiering, \textbf{R. Silva} and P. Dow, ``\textit{Acoustophoresis Device Having Improved Dimensions}'' U.S. Provisional Pat. Ser. No. 6038.US.00, filed 14 June 2017.}
\end{itemize}
